\Large Clustering Trips Identified from Automatic Number \\ Plate Recognition Camera Scans

### 2018-02-01 classification.tex
Used bits from other sections as the related work. Had to move figure 1 around so that the structure of the paper would not be affected as a result.

One direct application of trip data is unsupervised learning. Previous works have focused on identifying travel modes or purpose of trip from different sources of data, most notably: survey data, GPS data and mobile phone data~\cite{ODMobileData, ClusteringGPS}. Determining the distribution of travel modes is one of the fundamental steps in the four-stage model: an essential traffic modelling methodology for transportation planning~\cite{FourStepModel}. Although number plate data has been used in~\cite{Clustering}, to identify different categories of trips, these do not differentiate between private or public travel modes and focus for the most part on when the trips occurred. Therefore, we aim to identify groups of vehicles with similar trip patterns based on frequency and diversity of travel. This can be private vehicles, such as work-home commuters, transit vehicles like buses and taxis, or other types of vehicles such as delivery trucks.
%This in turn, may enable trip modes to be estimated
However, due to its limited coverage of the road network, it is not clear how well ANPR data can capture much the travel characteristics necessary to accurately describe the different groups.

Due to distinct traffic behavior during weekends, we chose to consider only trips occurring during weekdays. We thus used all number plate data collected during between the 6th and 24th of February and excluded data from the 2 weekends in between. Furthermore, as mentioned in section~\ref{s.trips}, we used fixed empirical values for $\Tau$, mostly due to time constraints. Table~\ref{t:trips-tau} displays the number of trips, average trip length and the proportion of trips of length one, for varying values of $\Tau$. The effect of incrementing $\Tau$ on resulting trips is clear: increased trip lengths and less trips containing just a single sighting. On the other hand, we did not set a value for $\tau$, but instead handled unplausible trips by filtering all sightings with confidence below 85\%. Duplicates were filtered after identifying consecutive sightings by the same camera occurring within the same trip. Clock synchronisation errors were provided in milliseconds with none exceeding 5 seconds. These were therefore ignored.

>>>>

One direct application of trip data is unsupervised learning. In this section we identify groups of vehicles with similar trip patterns based on frequency and diversity of travel. Clusters can represent private vehicles, such as work-home commuters, transit vehicles like buses and taxis, or other types of vehicles such as delivery trucks.
%This in turn, may enable trip modes to be estimated
%However, due to its limited coverage of the road network, it is not clear how well ANPR data can capture much the travel characteristics necessary to accurately describe the different groups.

Due to distinct traffic behavior during weekends, we chose to consider only trips occurring during weekdays. We thus used all number plate data collected during between the 6th and 24th of February and excluded data from the 2 weekends in between. Furthermore, as mentioned in section~\ref{s.trips}, we used fixed empirical values for $\Tau$, mostly due to time constraints. Table~\ref{t:trips-tau} displays the number of trips, average trip length and the proportion of trips of length one, for varying values of $\Tau$. The effect of incrementing $\Tau$ on resulting trips is clear: increased trip lengths and less trips containing just a single sighting. On the other hand, we did not set a value for $\tau$, but instead handled implausible trips by filtering all sightings with confidence below 85\%. Duplicates were filtered after identifying consecutive sightings by the same camera occurring within the same trip. Clock synchronisation errors were provided in milliseconds with none exceeding 5 seconds. These were therefore ignored.
